---
title: "STAT570 - Lecture2"
author: "Fulya Gökalp Yavuz"
format:
  html: 
    code-fold: true
    html-math-method: katex
  pdf:
    geometry: 
      - top=30mm
      - left=30mm
editor: visual
toc: true
number-sections: true
---

For this lecture, you need:

-   R version \>= 4.2.0

-   RStudio \>= 2023.03.1

# **Install R**

Download and install R for your operating system from <https://cloud.r-project.org/>.

### **Install R Studio**

Download and install RStudio Desktop from <https://posit.co/download/rstudio-desktop/>. This page should automatically offer you the version suitable for your operating system, but you can scroll down to find versions for all operating systems.

# Github Account

Register a GitHub account at [github.com](https://github.com/).

## **Check link between R and GitHub**

Configure your `user.name` and `user.email` for git in RStudio with:

``` r
usethis::use_git_config(
  user.name = "Charlie Brown",          # actual first and last name
  user.email = "brown@example.com"  # email associated with GitHub account
  )
```

Communicating with GitHub requires authentication with your GitHub account. This is achieved by creating and securely storing a Personal Access Token (PAT). The [Managing Git(Hub) Credentials](https://usethis.r-lib.org/articles/articles/git-credentials.html) vignette in the **`usethis`** ([Wickham et al. 2023](https://posit-conf-2023.github.io/pkg-dev/setup.html#ref-usethis)) package has details on using PATs, but for now the following should suffice.

Make sure you are connected to the GitHub Account from R. Before going to use_github(), we have to take the token by typing:

```{r, eval=FALSE}
usethis::create_github_token()
```

Write something to the decsription. Take the token from there and type in console:

```{r, eval=FALSE}
gitcreds::gitcreds_set()
```

Paste the token there and we are good to go.

Highly recommended book [Happy Git with R](https://happygitwithr.com/) for advice on setting up and using Git with R ([Bryan and Hester, n.d.](https://posit-conf-2023.github.io/pkg-dev/setup.html#ref-bryan)).

## Connect your RStudio to a GitHub Repository

Create you repository in **GitHub** and copy the link from Github Code\>\>Clone\>\>HTTPS. Then move back to **RStudio** and `File>>New Project>>Version Control>>Git>>Clone Git Repository` and paste your link to URL and create a new Project.

## References:

<https://posit-conf-2023.github.io/pkg-dev/setup.html#install-r-package-development-tools>

Github and RStudio: <https://resources.github.com/github-and-rstudio/>
